\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\usepackage{wrapfig}

\begin{document}
\begin{mla}{Paul}{English}{HUMA 1100-012}{Derek Bitter}{\today}{\textbf{Reflection Journal \#3 - Taoism}}

\section{What does Taoism ask us to be like?}

%%%%%%%%%%%%%%%
% What are the main principles or focus of confucianism?

%% - faithfulness
%% - sincerity
%% - virtue
%%   - stability
%%   - standards
%%     - moral
%% - social conduct
%%   - propriety, rules of
%% - wisdom, knowledge
%%   - teachable
%% - responsible
%% - honest
%% - openness
%% - reciproocity
%%    - Book XV Ch. XXIII - negative ethic vs. the positive ethic
%% - establish others
%% - loyalty
%%   - filial
%% - gravity, generosity, sincerity, earnestness, kindness
%% - self-control


%%%%%%%%%%%%%%%
% Are these teachings worth following?

% What problem could it cause to live these teachings, they are in
% general very useful, and morally right. Able to help anyone.

% nietzsche ``will to power'', may be the kind to argue against these
% beliefs, as though they are limiting.

% I liked the thoughts on how confucianism is political in a sense, as
% though in following you are bound to be favorable amongst a society

  
%%%%%%%%%%%%%%%
% Favorite passages?
  
%%%%%%%%%%%%%%%
% What is the end goal of Taoism?
  
% - opposites; appreciation
% - innocence of childhood
% - never overfulfillment

% yin - passive
% yang - aggressive


%%%%%%%%%%%%%%%
% What does it ask us to be like?

It asks us what we shouldn't be like, it shows us what there is
and describes what is good or great. It's not exactly straightforward,
and it tends to dance around every issue without explicitly stating
what is right or wrong for any particular individual. At least
sometimes, othertimes it does offer explicit advice.

Some of the principles that are valued include faithfulness,
sincerity, virtue, wisdom, knowledge, responsibility, honesty,
reciprocity, loyalty, and kindness among others. Many of the values
promote the best in humanity, and seek to uplift ourselves and those
around us.

The things that the Taoism asks us to be, or what not to be involve
a type of growth and transcendance over many of the worldly things we
cling to. It's similar to Buddhism and Hinduism in some parts, but
ultimately seems to differ in beliefs or mention of a deity or rebirth.
  
%%%%%%%%%%%%%%%
% Is there a single quality that helps us live all the rest?
  
%%%%%%%%%%%%%%%
% Does the lack of Deity in these teachings make a difference?



\end{mla}
\end{document}

