\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\usepackage{wrapfig}

\begin{document}
\begin{mla}{Paul}{English}{HUMA 1100-012}{Derek Bitter}{\today}{\textbf{Reflection Journal \#6 - Islam}}

\section{What are the characteristics of those who believe and those
  who do not?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% What things stand out that you did not expect?

% - jewish & christian references
% - black & white rules, strictness

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% What are the characteristics of those who believe and those who do
% not?

% - always believe, in all groups and types of company
% - work righteousness
% - worship none but allah
% - treat others with kindness
% - 83.
% - speak fair
% - steadfast in prayer
% - practice regular charity

% - people who submit to allah
% - jews, christians, muslims
% - belief in prophets, muhammed

Believers of Islam believe in both the Old Testament, and the New
Testament. They believe in the prophet Muhammad, and that the Qur'an
is holy revelation of God's will given through the prophet Muhammad.
They believe that they should work in rigteosnous, worship only Allah,
and should treat others with kindness. They believe they should speak
fair, be steadfast in prayer, and practice regular charity.

Though they seem to have many strict guidelines representing the rules
of their religion, they respect each other, and even those who are not
practicers of their religion. They respect their women, though the
roles can be perceived much differently from an outsiders perspective.

As an outsider, especially in the culture of the United States, we
tend to have a lot of negative bias, and stigmas regarding what this
religion teaches. Though the words they consider scripture, and their
practices don't seem to differ from what a majority of Christians and
Jewish followers believe and value. Our culture has recently
emphasized the unique differences, and extremist beliefs, which would
lead many to believe that it is a hateful or violent religion, which
it doesn't seem to present itself as. In fact, it's very much to the
contrary.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Is it possible to be inbetween?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% What characterizes righteousness?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% What is the difference between belief & knowledge?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% What is the value of each?


\end{mla}
\end{document}

