\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\usepackage{wrapfig}

\begin{document}
\begin{mla}{Paul}{English}{HUMA 1100-012}{Derek Bitter}{\today}{\textbf{Reflection Journal \#4 - Judaism}}

\section{What is this god like?}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% - What is the purpose of traditions?

%%     balance, stability, expectations, roles/function, no wandering,
%%     consistency, knowledge of self / identity, unity, faith,
%%     obedience, decisive, peace, harmony, community

%% - What is the harm or benefit in deviating from or not believing
%%   them?

%%     no growth, close-minded, separation, stagnation

%%             Breaking Off
%%     _harm_              _benefit_
%%     alienation          happiness
%%     regret              choice / freedom
%%     loss of identity    creation of identity
%%     struggles           gratified

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% - What is this god like?

This God feels much more vengeful, spiteful, controlling, emotional,
and strict. The rules are explicit, and with severe consequences. This
God makes himself known, and is highly respected. Even so much in that
his name is not fully represented in text or speach out of respect. He
speaks to the people, unlike other religions or gods.

In another sense he's still very concerned, loving, and understanding
of his people. Promising blessings and benefits for following his
word. He values his followers and hopes they grow, and share the story
amongst themselves and others.

He tests his people to see if they truly believe in him, or ensure
loyalty. He does it to teach his people, and confirm their own
feelings of him. This God feels much more like a concerned parent,
worried for the outcome of their children. Maybe even over-protective
in some senses.

Understanding the value of traditions, and rituals may also help us
understand why this God is like this, or even what he is like. The
Jewish people are very ritualistic, and follow their traditions
closely.


% - specific
% - jealous
% - concerned for people?

%%   - Why does he do what he does?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% - Why did God test Abraham?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% - What does it mean to fear God?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% - Why did the Israelites do what they did?


%% chatting about the golden calf
% - rose up to revel
% - acted preversely
% - stiff necked
% - quick to turn aside

\end{mla}
\end{document}

