\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\usepackage{wrapfig}

\begin{document}
\begin{mla}{Paul}{English}{COMM 1010-003}{Shirene
    McKay}{\today}{\textbf{Cultural Site Visit Notes}}

\section{Give a brief background of culture}

\begin{itemize}
  \item \textbf{Describe how you decided to visit this culture}
    I've never been to a government meeting, so I wanted to go. I
    wanted to see what it's like.
    
  \item \textbf{Give researched background on the culture}
    Most cities have city council, 
    
  \item \textbf{Tell us what you anticipated}
    I anticipated a dull meeting with old people.
    
\end{itemize}

\section{Describe communication}

\begin{itemize}
  \item \textbf{Share specific examples of communication experiences,
    own feelings} \\
    It's a very moderated and structured meeting, with a very specific
    vocabulary used to control discussion.
    
  \item \textbf{Use communication vocabulary from the chapter} \\
    low-context, not much diversity.
    
  \item \textbf{Share artifact} \\
    It's a printed meeting agenda! Clearly Sandy city is on the ball,
    they've still got 2012 in there.
    
\end{itemize}

\section{Analysis}

\begin{itemize}
  \item \textbf{Suggest how a person might prepare to make a visit to
    this site enjoyable} \\
    Visiting a city council meeting is not a particularly joyous
    occasion, it would seem that most people will go there primarily
    to argue a point or get support in regards to some issue. I would
    suggest reviewing the council meeting agenda beforehand, they're
    usually always posted on the city websites. This will clue you in
    to the topics that will be reviewed and voted on by the council
    members. You may want to regularly check these agendas to see if
    issues relating to you ever arise.
    
  \item \textbf{Tell us what you learned} \\
    I learned a little bit about the seperation of the council side of
    city government from the administration side, as one person tried
    to argue for a permit, which was repeatedly declared as an
    administrative issue, and not for debate in the meeting.

    I learned a bit about the specialized language that is used to
    moderate and control discussion.
\end{itemize}

%%%%%%%%%%%%
\section{NOTES}

mayor dolan

- guy from pleasent grove handing out budget awards

catheter award?

- citizens comments

-- cit (josh) represents firksy: half-marathon to end in sandy

big cottonwood marathon 

- council items

ordinance 1304

ammending title 15 chapter 13


matt schadel on a temporary work permit

150 days

on temporary business in a vacant lot

christmas trees

90th S and State

is it appropriate to ask questions about topics?

The girl Kris looks to be drinking a PBR

\pagebreak
\section{An excerpt from ``So Long, and Thanks for All the Fish'' by
  Douglas Adams, included for no reason whatsoever}

\begin{quotation}
  
[An extraterrestrial robot and spaceship has just landed on earth. The
  robot steps out of the spaceship...]

``I come in peace,'' it said, adding after a long moment of further
grinding, ``take me to your Lizard.''

Ford Prefect, of course, had an explanation for this, as he sat with
Arthur and watched the nonstop frenetic news reports on television,
none of which had anything to say other than to record that the thing
had done this amount of damage which was valued at that amount of
billions of pounds and had killed this totally other number of people,
and then say it again, because the robot was doing nothing more than
standing there, swaying very slightly, and emitting short
incomprehensible error messages.

``It comes from a very ancient democracy, you see...''

``You mean, it comes from a world of lizards?''

``No,'' said Ford, who by this time was a little more rational and
coherent than he had been, having finally had the coffee forced down
him, ``nothing so simple. Nothing anything like to straightforward. On
its world, the people are people. The leaders are lizards. The people
hate the lizards and the lizards rule the people.''

``Odd,'' said Arthur, ``I thought you said it was a democracy.''

``I did,'' said ford. ``It is.''

``So,'' said Arthur, hoping he wasn't sounding ridiculously obtuse, ``why
don't the people get rid of the lizards?''

``It honestly doesn't occur to them,'' said Ford. ``They've all got the
vote, so they all pretty much assume that the government they've voted
in more or less approximates to the government they want.''

``You mean they actually vote for the lizards?''

``Oh yes,'' said Ford with a shrug, ``of course.''

``But,'' said Arthur, going for the big one again, ``why?''

``Because if they didn't vote for a lizard,'' said Ford, ``the wrong
lizard might get in. Got any gin?''

``What?''

``I said,'' said Ford, with an increasing air of urgency creeping into
his voice, ``have you got any gin?''

``I'll look. Tell me about the lizards.''

Ford shrugged again.

``Some people say that the lizards are the best thing that ever
happened to them,'' he said. ``They're completely wrong of course,
completely and utterly wrong, but someone's got to say it.''
\end{quotation}

\end{mla}
\end{document}

