\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\usepackage{wrapfig}
\usepackage{dramatist}


% overwrite double spacing
\linespread{1}



\begin{document}

\begin{mla}{Paul}{English}{COMM 1010-003}{Shirene
    McKay}{\today}{\textbf{Cross-Cultural Face-Negotiation Roleplay}}

\Character[Richard Miller - A male security officer]{Richard}{rich} % define characters
\Character[Kiyoko Ozaki - A female rehabilitation nurse]{Kiyoko}{kiyoko}
\Character[Paul English - A software engineer]{Paul}{paul}

\scene[]

\StageDir{
    \begin{center} Dreamscape Nursing \& Care Facility - After hours; 
    Kiyoko, a female rehabilitation nurse from Japan seeks to get into her office building and retrieve her soon to be late tax documents which she forgot after her shift. Having forgotten her badge at home, Richard, a middle-aged security officer tries to direct her to return the next day, when the business is open.
     \end{center}
}

\begin{drama}

\kiyokospeaks \dots Hello?
\richspeaks \emph{Snoring \dots}
\kiyokospeaks Excuse me \dots Hello?
\richspeaks \emph{Slight pause in breathing \dots Still snoring}
\kiyokospeaks Hello!
\richspeaks \dots
\StageDir{Kiyoko rings the bell found on the desk. Richard is alarmed}
\richspeaks \dots Erm, hello! \dots Sorry about that, sleeping comes so naturally to me, I could do it with my eyes closed. How can I help you?
\kiyokospeaks Hi, I was hoping I could get in the building. I'm a nurse here, I left some of my belongings there from today's shift.
\richspeaks I'll need to see your badge.
\kiyokospeaks I think I left it at home.
\richspeaks Oh, um \dots I know you usually \emph{call the shots}, but I'm sorry ma'am I can't let you in unless I see your badge.
\kiyokospeaks Oh please, there must be something you can do. It's just some papers that I have left at my desk.
\richspeaks Well Ma'am, our company is contracted to keep this building secure, I can't let you in unless you have appropriate credentials.
\kiyokospeaks Maybe you can look me up in the employee roster? I have my State ID.
\richspeaks I'm sure you're in there, but there are no guarantees that you weren't fired today. I still need to see your badge.
\kiyokospeaks Maybe you can fetch my things for me?
\richspeaks Wow, you nurses really love \emph{needling} people, don't you? I can't do that, you'll have to return tomorrow. What's in there that you have to get at anyways?
\StageDir{Embarrased to be so late in filing her tax returns, Kiyoko lies.}
\kiyokospeaks Um, I have some poetry in there.
\richspeaks A poet? Well, wouldn't you \emph{know it} \dots Sorry, I can't get your poems Ma'am.

\paulspeaks Ugh\dots I can't think up a cheesy way to relate it to poetry tax.

\richspeaks A flat-rate poetry tax sure would be a \emph{per-verse} form of greed.



\StageDir{Kiyoko leaves completely unimpressed and annoyed.}

\end{drama}

\end{mla}
\end{document}

