\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\usepackage{wrapfig}

\begin{document}
\begin{mla}{Paul}{English}{COMM 1010-003}{Shirene McKay}{\today}{\textbf{Video Self-Evaluation}}

\section{Appearance}
% (clothes, hair, accessories, posture)
I wore a plain t-shirt, I could have dressed up, but I chose the
t-shirt to try and highlight the cultural difference, and emphasize
why I chose a city council meeting in particular. I can't say my hair
was all that great, the last time I went to the barbershop, the girl
there left the front of my hair a little bit longer than it should
have been, leaving it to awdwardly curl and stand out. I could have
gotten that fixed, but never worried about it. I really should just
shave it all, I'm probably going bald anyways.

\section{Organizational Pattern}
% (introduction, preview, conclusion, signposts, transitions,
% support material, flow, word choice)
I could have worked a bit on my organization. I had notes on the
meeting, and notes on what I was going to basically cover, but while
presenting I didn't follow much of a structured, or planned outline. I
could have taken more time to ensure that I matched the time limits,
and flowed from one point to the next highlighting the key parts of
the meeting.

\section{Vocal Qualities}
% (pitch, pause, fillers, projection, variation)
Though I presented with some confidence I could have improved my
projection and clarity of voice. I wasn't quiet, but I didn't practice
or worry much about projection, and that is noticeable. I tended to
use a lot of fillers, which is something we all do, however if I would
have organized a bit better, and practiced a few times, I could have
curbed this behavior. Some of the words I could have removed, ``umm'',
``I mean'', ``just'', ``kind of''.

\section{Delivery}
% (gestures, body movement, eye contact)
I used my hands a lot, making plenty of gestures, maybe this was
distracting, it was probably ok. During a few points of the
presentation, I scratched at my nose, and covered my mouth. If I were
playing poker, you can bet on it, that's my tell. While presenting I
felt like I was looking at the audience, however upon review it looks
as though I was staring above the audience, and darting back and forth
a bit. It was very easy to tell when I was recalling a fact or memory,
by watching my eyes dart up to the top of my head inbetween staring at
my notes. In addition to the filler words I used, I tended to shrug a
bit along with them.

\section{Visual Aid}
% (artifact, design, way it was used)
I had the meeting agenda to pass around. It was simple, one page,
showed what happened in the course of the meeting. I just passed it
around, and it was probably ok. I could have created something to go
along with the history of the city council meeting, or a similar
visual aid, though I feel the meeting agenda provided enough as it was.

\section{Audience Connection}
% TODO (pathos, ethos, logos)
Pathos: I feel as though the audience caught on to my personality. I
was able to joke a bit, and share the quirks I found with the people
at the meeting. The audience laughed along, understanding the
awkwardness.

Logos: I ran through meeting topics pointing out the highlights. A
city council meeting is about logical agreements, so this was present
as I shared the outcomes and reasoning which went on for the duration
of the city council meeting.

Ethos: I tried to emphasize that I'm not really all that political, I
wanted to show my viewpoint, and get the audience to see what it was
like for me to be there. I shared a bit of my personal background, and
about how I felt while there.

\section{Strenths}
% (what worked well for you)
I would say, that even though I felt nervous, I presented clearly and
calmly. I made special effort to speak slowly so that I didn't sound
like a chipmunk while up at the dais. My use of gestures, and telling
of the scene was also a part of my presentation that I felt I was
strong in.

\section{Areas to Improve}
% (plans for areas would like to work on for your next
% presentation)
I think the greatest thing I could work on is organizing my thoughts,
and practicing. Like I mentioned earlier I had a lot of fillers, and
obvious lack of organization or flow. With a better outline and some
practice in front of a mirror or with friends I could have easily
improved my presenting tenfold or more.

\end{mla}
\end{document}

