\documentclass[12pt,letterpaper]{article}
\usepackage{amsmath}

\title{Chem 1010-009 Homework}
\date{\today}
\author{Paul English}

\topmargin=0cm
\oddsidemargin=0cm
\textheight=22.0cm
\textwidth=16cm
\parindent=0cm
\parskip=0.15cm
\topskip=0truecm
\raggedbottom
\abovedisplayskip=3mm
\belowdisplayskip=3mm
\abovedisplayshortskip=0mm
\belowdisplayshortskip=2mm
\normalbaselineskip=12pt
\normalbaselines


\begin{document}

\maketitle

\begin{enumerate}

\setcounter{enumi}{8} % 9
\item 

Give the name of each of the following simple binary ionic compounds.

\begin{enumerate}
\item $NaBr$ - Sodium bromide\\
\item $MgCl_2$ - Magnesium(II) chloride\\
\item $AlP$ - Aluminum phosphoride\\
\item $SrBr_2$ - Strontium(II) bromide\\
\item $AgI$ - Silver iodide\\
\item $K_2S$ - Potassium sulfide\\
\end{enumerate}

\setcounter{enumi}{17} % 18
\item 

Write the name of each of the following binary compounds of nonmetallic elements.

\begin{enumerate}
\item $ClF_5$ - Chlorine pentaflouride\\
\item $XeCl_2$ - Xeon dichloride\\
\item $SeO_2$ - Selenium dioxide\\
\item $N_2O_3$ - Dinitrogen trioxide\\
\item $I_2Cl_6$ - Diiodide hexachloride\\
\item $CS_2$ - Carbon disulfide\\
\end{enumerate}

\setcounter{enumi}{18} % 19
\item 

Name each of the following binary compounds, using the periodic table to determine whether the compound is likely to be ionic (containing a metal and a nonmetal) or nonionic (containing only nonmetals).

\begin{enumerate}
\item $Fe_3P_2$ - Iron phosphoride\\
\item $CaBr_2$ - Calcium bromide\\
\item $N_2O_5$ - Dinitrogen pentaoxide\\
\item $PbCl_4$ - Lead(IV) chloride\\
\item $S_2F_{10}$ - Disulfur deciflouride\\
\item $Cu_2O$ Copper oxide\\
\end{enumerate}

\setcounter{enumi}{26} % 27
\item 

Complete the following list by filling in the missing names or formulas of the oxyanions of chlorine.

\begin{enumerate}
\item $ClO_4^-$ -  perchlorate\\
\item $ClO^-$ - hypochlorite \\
\item $ClO_3^-$ -  chlorate \\
\item $ClO_2^-$ - chlorite \\
\end{enumerate}

\setcounter{enumi}{33} % 34
\item 

Give the name of each of the following polyatomic ions.

\begin{enumerate}
\item $NH_4^+$ - Ammonium\\
\item $H_2PO_4^-$ - Dihydrogen phosphate\\
\item $SO_4^{2-}$ - Sulfate\\
\item $HSO_3^-$ - Hydrogen sulfite\\
\item $ClO_4^-$ - Perchlorate\\
\item $IO_3^-$ - Iodate\\
\end{enumerate}

\setcounter{enumi}{38} % 39
\item 

Name each of the following acids.

\begin{enumerate}
\item $HCl$ - Hydrochloric acid\\
\item $H_2SO_4$ - Sulfuric acid\\
\item $HNO_3$ - Nitric acid\\
\item $HI$ - Hydroiodic acid\\
\item $HNO_2$ - Nitrous acid\\
\item $HClO_3$ - Chloric acid\\
\item $HBr$ - Hydrobromic acid\\
\item $HF$ - Hydroflouric acid\\
\item $HC_2H_3O_2$ - Acetic acid\\
\end{enumerate}

\setcounter{enumi}{45} % 46
\item 

Write the formula for each of the following compounds that contain polyatomic ions. Be sure to enclose the polyatomic ion in parentheses if more than one such ion is needed to balance the oppositely charged ions.

\begin{enumerate}
\item ammonium acetate - $NH_4C_2H_3O_2$\\
\item ferrous hydroxide - $FeOH$\\
\item cobalt(III) carbonate - $Co_2(CO_3)_3$\\
\item barium dichromate - $BrCr_2O_7$\\
\item lead(II) sulfate - $PbSO_4$\\
\item potassium dihydrogen phosphate - $KH_2PO_4$\\
\item lithium peroxide - $Li_2O_2$\\
\item zinc chlorate - $ZnClO_3$
\end{enumerate}

\end{enumerate}

\end{document}