\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\usepackage{wrapfig}

\begin{document}
\begin{mla}{Paul}{English}{ENG 2010-002}{Professor Argyle}{\today}{\textbf{Letter Of Evaluation}}

%%% 

% Each student will write an individual Letter of Evaluation. 
% The purpose of this letter is to evaluate the collaboration of your group for the duration of the project. 
% In this evaluation consider your own contributions as well as the contributions of your group-mates. ? page. 

In working with my group this semester I found our collaboration to be adequate and helpful. We were a small team, only having a group of 3 members, but we seemed to be focused on the topic, and all made strides to complete the coursework we needed. When working individually we all had clear angles to focus on that allowed us to differentiate our work. When working on the group assignments it was easy to choose our projects without conflict.

When working together and reviewing each others work I benefitted from the alternative viewpoints that were given by my group members. As I read through their papers, I learned and improved my work. Though, Arturo was a absent more often he still was included and helped out. Joshua was always here and almost always had work ready for review when we were trading our papers with each other.

I think our group worked well together as individuals, and when we collaborated on work, like the presentation slides and the community cover letter we worked quickly and did what was needed to do. 

Oh yeah, there was that one guy, who was in our group for about a day. I can't say he collaborated much, if at all.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{workscited}

% http://www.nottheanswer.org/2012/07/01/offshore-drilling-plan-for-2012-2017-released-by-obama-administration/
% http://public.surfrider.org/files/Surfrider\_2012\_2017\_Oil\_Gas\_PEIS\_Jan2012\_Final.pdf
% http://www.boem.gov/5-year/2012-2017/
% http://hotair.com/archives/2012/06/30/the-obama-administrations-five-year-drilling-plan-hint-its-underwhelming/

%\end{workscited}
\end{mla}
\end{document}
