\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\begin{document}
\begin{mla}{Paul}{English}{ENG 2010-002}{Professor Argyle}{\today}{Position / Proposal}

%\section{Position}
A position essay explains multiple sides of an issue and argues for one side over the others.  Your goal is to explain the various sides of the issue and highlight the differences between these views.  Use solid reasoning and factual evidence to persuade your readers to adopt your point of view.  Your position should identify the problem, make claims that you will support, provide a summary of your understanding of the issue, include a point-by-point discussion of the limits of the various views about the issue, and establish and support your own position about the issue.

- identify a problem
- explain multiple sides of the issue
- include point by point discussion of the limits of the various views
- establish and support own position
- use solid resigning and factual evidence to persuade readers

The environment is in bad shape. No, It's all good.
Fossil fuel usage needs to stop soon. No, that current fossil fuels are good enough for now while we improve other options.
We all impact the environment. No, That I don't have much of an impact on the environment
The data is accurate. No, The data is skewed \& biased

%\subsection{Introduction}
%\subsection{Summary}
%\subsection{Understanding}

%\section{Proposal}
A proposal essay moves beyond reporting facts (the report) or arguing for a particular perspective in order to persuade the reader to take some kind of action in relation to your issue. The proposal will build on the position you have established and should, therefore, persuade the reader that it is indeed a problem that needs to be addressed, and then lay out a specific proposal to solve the problem.  It should offer a conclusion that looks to the future and stresses the importance of taking action.

- build on position
- persuade reader that it is indeed a problem
- lay out oblem
- offer a conclusion that looks to the future and stresses the importance of taking action

The purpose of my proposal is to curb environmental damage by
suggesting alternative consumer practices and conservation of existing
resources. 

- Drive, fly, \& in general commute less. Fossil fuels make up one of
  the largest contributers to environmental degradation
- Seek out alternative energy sources in your own household. Personal
  solar energy \& water heating. Gardening. Recycling trash, and
  composting. 
- Speak up to political and government leaders about energy and
  environment related issues
- Keep your older phones and computers longer in order to prevent
  wasteful consumption.

- include images
- include citations
%\subsection{The Problem}
%\subsection{The Plan}
%\subsection{The Points}

%\section{Conclusion}

\begin{workscited}

\bibent
Goddard Institute for Space Studies. ``National Aeronautics and Space Administration." Data.GISS:GISS Surface Temperature Analysis (GISTEMP). NASA, 17 Feb. 2012. Web. 26 June 2012. $<$http://data.giss.nasa.gov/gistemp/$>$.

\bibent
Heinberg, Richard, and Daniel Lerch. \textit{The Post Carbon Reader: Managing the 21st Century's Sustainability Crises.} Healdsburg, CA: Watershed Media, 2010. Print.

\bibent
J¿rgensen, Michael S¿gaard, and Ulrik J¿rgensen. ``Green Technology Foresight Of High Technology: A Social Shaping Of Technology Approach To The Analysis Of Hopes And Hypes." Technology Analysis \& Strategic Management 21.3 (2009): 363-379. Academic Search Premier. Web. 19 June 2012.

\bibent
Levi, Maurice D., and Barrie R. Nault. ``Converting Technology to Mitigate Environmental Damage." Management Science 50.8 (2004): 1015-030. Print.

\bibent
McManus, M.C. ``Environmental Consequences Of The Use Of Batteries In Low Carbon Systems: The Impact Of Battery Production." Applied Energy 93. (2012): 288-295. Academic Search Premier. Web. 21 June 2012.

\bibent
Plous, Evan ``Production and Use of Biodegradable Materials for Incorporation in a Non-Toxic, Eco-Friendly Battery." Kansas Academy of Science 110, (2007): 116-124. JSTOR. Web. 21 June 2012.

\bibent
UPS. Public Relations. ``Right Turn at the Right Time." UPS Pressroom. UPS, 2007. Web. 21 June 2012. $<$http://pressroom.ups.com/About+UPS/UPS+Leadership/Speeches/\\D.+Scott+Davis/Right+Turn+at+the+Right+Time$>$.

\pagebreak
\bibent
Wal-Mart. ``Wal-Mart Surpasses Goal To Sell 100 Million Compact Fluorescent Light Bulbs Three Months Early." Wal-Mart Corporate. Wal-Mart, 2 Oct. 2007. Web. 21 June 2012. $<$http://www.walmartstores.com/pressroom/news/6756.aspx$>$ .


\end{workscited}
\end{mla}
\end{document}
