\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\usepackage{wrapfig}

\begin{document}
\begin{mla}{Paul}{English}{ENG 2010-002}{Professor Argyle}{\today}{\textbf{Reflection Essay}}

%REQUIREMENTS
%%% 2-3 pages

%%% address course objectives
%  How has the work you've done this semester helped you

%%% address how you used peer review suggestions made by your peers
% What kind of comments did you find most helpful? 
Though understanding and having grammar and spelling mistakes were useful in creating the writing for this course, I found that comments on the theme, structure, and flow of my papers was the most beneficial.
% How have your peers helped you improve your writing this semester?
I think I've learned the most about focused writing styles, in the past I've often only followed simplistic structures, or just free-written. Having a prescribed structure to the papers I've written has helped to metaphorically expand my language arsenal.
% What are 2-3 suggestions you made for your peers?
When working with my peers, my suggestions most often referenced their content. Though I would note grammatical errors, or spelling mistakes, I was always most interested in what they were writing about and why. It shouldn't be too shocking therefore that my corrections or suggestions often centered around the writers topic. In most cases I just asked questions about the papers I reviewed.
% What do you see as your greatest strength as a peer reviewer?
I suppose it's easy for me to find interest whatever it was they were writing. It's hard to provide quality feedback if you don't really care too much about what you recently read.
% How has doing peer review improved your own writing?
Reviewing has helped me to expand in my own writing. I'm able to read and decipher other author's voice, and I find that characteristics that I value in their style sometimes show through in the things I write.

%%% discuss specific changes you made as you revised your documents
% What changes did you make in your documents?
I found that some of the automatic spell check features included in my operating system tended to augment things I wrote in a few unexpected ways. It was fairly common for me to find correctly spelled homonyms which needed to be changed to preserve the meaning I had initially intended. Even in writing this reflection essay, I found my editor aggressively fixing words I typed.

This is absurdly useful when I misspell, however the greedy nature of this algorithm seems

% TODO run writing bash scripts against these papers. uofu guy

% Cite specific changes.

%%% describe the process of putting together  your final portfolio
% How did you decide what pieces to use?
% What do you see as the greatest strength of your writing & portfolio?
% If you went through the process again, what would you do differently?

%NEEDS
%* 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{workscited}

% http://www.nottheanswer.org/2012/07/01/offshore-drilling-plan-for-2012-2017-released-by-obama-administration/
% http://public.surfrider.org/files/Surfrider\_2012\_2017\_Oil\_Gas\_PEIS\_Jan2012\_Final.pdf
% http://www.boem.gov/5-year/2012-2017/
% http://hotair.com/archives/2012/06/30/the-obama-administrations-five-year-drilling-plan-hint-its-underwhelming/

%\end{workscited}
\end{mla}
\end{document}
