\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\usepackage{wrapfig}
\usepackage{setspace}

\begin{document}

\begin{mla}{Paul}{English}{HUMA 1100-012}{Derek
    Bitter}{\today}    
    {\textbf{Reflection Journal - Diary Excerpts}}

\section*{What does it take to stand against crimes of humanity?}

In the reading, ``Diary Excerpts'' we find short journal entries from a German military officer who stood against the injustices of life that Hitler's Germany created. In the face of power and social coercion he wrote about the things he knew were wrong, and standing against it how he was able. Many times we'd like to think we would be able to go against the tide of a movement that surrounds us. To stand in rebellion towards the things that we can tell are wrong and inhumane. Often times it's not that easy, but we can always reflect on what's happening around us and lean on our own personal set of moral's the best we are able.

Captain Wilhelm, the author of these journal articles, shares with us the atrocities that he faces. He says, ``Evil and brutality lurk in the human heart. If they are allowed to develop freely they flourish, putting out dreadful offshoots, the kind of ideas necessary if the Jews and Poles are to be murdered like this. What cowards we are, thinking ourselves above all this, but letting it happen.'' On his own, as a member of the society that was promoting these evils, he scribed his true thoughts of the process, and noted how we are cowards in letting it happen. It probably wasn't easy to oppose such a powerful and dangerous force that's surrounding you, it's certain to get you killed if found out. Still not opposing it, or letting it happen by his words would be cowardice.

How did this Captain become so enlightened of the atrocities around him? Did the other soldiers feel the same way, and just avoid writing these thoughts down, or not speaking up? Judging by the fact that so much evil occurred we can infer that it was no easy task. The problems crept into they're actions slowly, flourishing far beyond the point that anyone would ever consider morally or ethically right. Hard to believe, but it happened. In order to stand against issues like this we have to avoid a level of brain washing really.


\end{mla}
\end{document}

