\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\usepackage{wrapfig}
\usepackage{setspace}

\begin{document}

\begin{mla}{Paul}{English}{HUMA 1100-012}{Derek
    Bitter}{\today}    
    {\textbf{Reflection Journal - Our Freedoms and Rights}}

\section*{What are the differences between a Right and a Freedom?}

Sometimes it's hard to differentiate what makes something a right, as opposed to a freedom. Our rights are delicately intertwined with the freedoms we exercise. Rights are fundamental, and lay the groundwork for most of our freedoms and many things we may take for granted each day. Usually our natural human rights are uncontested and we are given a chance to exercise those rights. The reading makes note of several of these; to work, to have food and shelter, to have basic equality, among others. Many of these things we are always provided the opportunity to do, and to have. By always allowing people rights we keep our society humane at some level. Freedoms can cover a larger basis, though they might not differ too much. A freedom is more often seen as a luxury item, sometimes more fragile or fleeting. Many of us have freedoms, though it's possible to abuse those freedoms and to be stripped of them. Being put in jail, we would lose many of the freedoms which we would have had, but in many cases we don't lose our rights to the necessities of life. Though our rights can be hampered in many ways, even in the cases where a person might abuse their general freedoms, their rights are still likely to be afforded them. 

Both rights and freedoms come with a cost of ownership. We may have the right to travel, but it's unwise to travel onto certain private or government land uninvited. We may have the right to adequate food, and nourishment but if we steel food, we're likely to be disciplined for that action. We can't fall back on one of our rights as an excuse for an action we have taken that has caused harm to someone else, and our freedoms are usually restricted when that happens.

Over time what we view as a right and a freedom change, but many of them stay the same. By encouraging certain rights we help to strengthen our culture, and improve everyone's quality of life.


\end{mla}
\end{document}

