\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\usepackage{wrapfig}
\usepackage{setspace}

\begin{document}

\begin{mla}{Paul}{English}{HUMA 1100-012}{Derek
    Bitter}{\today}    
    {\textbf{Reflection Journal - Great Society Speech}}

\section*{Why is education an important factor to ``A Great Society''?}

In the reading by Lyndon B. Johnson we are introduced to the concept of ``A Great Society,'' and what components make up this idealistic view of America which we should be working towards. Johnson highlights several very strong points that make up what he perceives to be a great society including improving our cities, countryside, and education. Education is a particular point which can be highlighted, though much of what is said is important. The right emphasis on education sets the tone for the long-term future, and ultimately shapes the generation that will replace us.

It's important to value education individually, but in the sense that Johnson seems to be representing it, we must also improve and enable the education system for the kids we raise. Education is the one thing that can help improve our lives long after were able to make a difference. At some point we all have to retire our work and hand the reigns over to people who are now more capable than us, usually younger. A country that's educated is usually one that cares about the world around them.

Education helps us explore the new and interesting issues we face as we grow and change. We will never run into the exact same issues of past generations, so we have to know about the current state of affairs in the world. However sometimes the issue will be similar, in which case falling back to known history can make a great affect. Education equalizes and humbles many of us. It helps to overwrite prejudice, bias, and even hate we might have had. Every society stands to be great by supporting education.


\end{mla}
\end{document}

