\documentclass[12pt,letterpaper]{article}
\usepackage{mla}
\usepackage{wrapfig}
\usepackage{setspace}

\begin{document}

\begin{mla}{Paul}{English}{HUMA 1100-012}{Derek
    Bitter}{\today}    
    {\textbf{Reflection Journal - Letter to Birmingham Jail}}

\section*{Why is it important to non-violently defend certain freedoms?}

In the response letter written by Martin Luther King Jr. to the Alabama Clergymen, a strong point is made about actively defending the rights, equalities, and freedoms of the African American people through the use of passive protest. Passive in the sense that they weren't looking to aggressive, violent, or to war over their cause. King stood for a peaceful uprising, and so did the movement that was being stirred up at that time. What about this situation, and cause made it important for them to remain peaceful? Why would they suffer various legal issues, aggressive attacks, and other persecutions?

When suffering for the defense of civil liberties, there really is only one way to approach. If you were to fight violence with violence you're likely to only escalate the fight until one side or the other is defeated. It would become instantly hypocritical to defeat an opponent given the original cause, and reasons for fighting to begin with. It would only prove the point of the aggressors, in this case the white-supremacy movement. There could be no winner in a violent fight for human liberties and rights, since we would devolve completely throwing aside whatever it is that makes us human.

Much of the argument that is presented by MLK details how justice can't always be arrived at by letting the time take care of it. 	``Time is neutral,'' he says in reference to the fact that if they don't stand up for their rights now, and instead idly sit by in an attempt to be peaceful about the situation, they will inevitably arrive at an outcome where the more active party in this situation wins. So in order to defend, they have to take action against the injustices they face, but they have to do it in a way that proves their cause. It is the only right action for them to take. It is often the only right action for any of us to take when presented with such a large disparity in equality, as is the case with racism.


\end{mla}
\end{document}

